Methods and Results

### 2021-05-01 ms.Rmd
Adding new figure for HarmType. Need to add in estimates and PIs etc, maybe just use orchard for it, but lets see

#### Female fitness is less compromised in species with reversed sexual size dimorphism (SSD)

>>>>

```{r maleharn, fig.width=6, fig.height=4.5}
ggplot(data, aes(x = Harm_type, y = SMDH, size = 1/sqrt(v_SMDH), fill = Harm_type, colour = Harm_type)) + geom_violin(alpha = 0.2) + geom_point() + 
  geom_jitter(width = 0.1) + 
  theme_bw() + 
		theme(legend.background = element_blank(),
			           legend.key = element_blank()) + 
  labs(x = "Harm Type", y = "SMDH", size = TeX("Precision $\\left(\\frac{1}{\\sqrt{v_{SMDH}}}\\right)$")) +
  scale_x_discrete(labels = c("Both", "Direct", "Indirect")) +
  guides(size = guide_legend(override.aes = list(linetype = 0))) + 
   scale_colour_discrete(guide = FALSE) +
  scale_fill_discrete(guide = FALSE)
```
#### Female fitness is less compromised in species with reversed sexual size dimorphism (SSD)
